Automatically generated NE tagged corpora for English and Hungarian

### 2012-06-29 paper/jeju_presentation.tex
Copied "Motivation" part from the paper.

\subsection*{Motivation}
\begin{frame}{Blabla}
\end{frame}
\subsection{Articles to Entities}
\begin{frame}{Problem Statement}
  In many real world applications the problem is to predict outputs with a nontrivial structure given some inputs.
  \vfill
  Example: \textit{\small It was love at first sight.}
  \vfill
\end{frame}

>>>>

\subsection*{Motivation}
\begin{frame}{Motivation}
  \begin{itemize}
  \vitem Our goal is to create a large NE annotated corpus, automatically
        generated from WP articles.
  \vitem Our method is similar to Nothman et al. (2008)
  \vitem The process consists of four steps:
    \begin{enumerate}
    \vitem Classify WP articles into entity classes.
    \vitem Parse WP and split articles into sentences.
    \vitem Label named entities in the text.
    \vitem Select the sentences for inclusion in the corpus.
    \end{enumerate}
  \end{itemize}
\end{frame}

\subsection{Articles to Entities}
\begin{frame}{Problem Statement}
  In many real world applications the problem is to predict outputs with a nontrivial structure given some inputs.
  \vfill
  Example: \textit{\small It was love at first sight.}
  \vfill
\end{frame}

\subsection{}
\subsection{}
\subsection{}
